A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise FBDDs

In this last section, some alternative representations of BDDs are discussed
briefly, i.e. FDDs, ZBDDs and BEDs. These representations were introduced primarily
because the OBDD representation is insufficient for some problems of practical
relevance. Bryant~\cite{BRYANT95} already reviewed most alternative represenations
but some were introduced after this overview, e.g. the
\textit{Binary Expression Diagrams} introduced by Andersen and
Hulgaard~\cite{ANDERSEN97} in 1997.

@@

Although the variable ordering problem is well-studied, OBDDs have some severe
limitations for some classes of Boolean functions, regardless of the variable
ordering chosen, e.g. integer multiplication (see Section~\ref{sec:limitations}).
One way researchers tried to overcome this issue is relaxing the variable ordering
requirement. \textit{Free BDDs} (\textit{FDDs}) is one proposed approach. FDDs
do not require the variables in the BDD to be ordered but, instead, require that
each variable only occurs once along any path (starting from the root node).
Hence, FDDS are also referred to as \textit{1-time branching programs}. Moreover,
FDDs have the same desirable algorithmic properties as OBDDs~\cite{BRYANT95}. \tbr

>>>>

In this last section, some alternative representations of BDDs are discussed
briefly, i.e. FBDDs, ZBDDs and BEDs. These representations were introduced primarily
because the OBDD representation is insufficient for some problems of practical
relevance. Bryant~\cite{BRYANT95} already reviewed most alternative represenations
but some were introduced after this overview, e.g. the
\textit{Binary Expression Diagrams} introduced by Andersen and
Hulgaard~\cite{ANDERSEN97} in 1997.

@@

Although the variable ordering problem is well-studied, OBDDs have some severe
limitations for some classes of Boolean functions, regardless of the variable
ordering chosen, e.g. integer multiplication (see Section~\ref{sec:limitations}).
One way researchers tried to overcome this issue is by relaxing the variable
ordering requirement. \textit{Free BDDs} (\textit{FBDDs}) is one proposed
approach. FBDDs do not require the variables in the BDD to be ordered but,
still, require that each variable only occurs once along any path (starting from
the root node). Hence, FBDDS are also referred to as
\textit{1-time branching programs}. Moreover, FBDDs have the same desirable
algorithmic properties as OBDDs~\cite{BRYANT95}.
